

\documentclass{my_cv}

\begin{document}

\name{Nadia Noormohamed}
\longcontact{Location: Manchester}{nadianoormohamed96@gmail.com}
{Mobile: 07476342168}\url{linkedin.com/in/nadianoormohamed}{}

\section{Education}
\datedsubsection{University of Manchester, B.sc Computer Science}{2015--2019}


\workitemSix
{First Year overall grade: 2:1 (65\%)}
{1st Year Team Project:  
Built and tested a web application called Coffee Time as a team that derived results (coffee shops) based on the filter options chosen e.g type of seating, within the radius selected.}
{Built the front end of the application. Used HTML, CSS, Javascript and Bootstrap. Used Git to control the versions of the application.}
{Presented the plan and finished result of the application as a team}
{Java Module: Applied Java throughout coursework. Learnt concepts such as testing, data structures, polymorphism and inheritence. The highlight of the course was to create classes to complete a snake game.}
{Stendhal project: Currently working on a large existing code base of the game: Stendhal, the project so far has involved testing to reveal errors, pinpointing errors in the code from the large numbers of classes present and proavtively eradicating the bugs in code. In addition to this, the project has exposed me to concepts such as abstraction and understanding large bodies of code written by others.}

\datedsubsection{Loreto Grammar Sixth Form  
}{2012--2014}

\workitemOne
{A Levels: Mathematics (C), Biology (C), Chemistry (C)
}

\datedsubsection{Stretford High School
}{2007--2012}

\workitemOne
{10 GCSE'S: A-C
}




\section{Employment History}

\datedsubsection{Operations-Executive, HSBC IDVA}
{Jun 2017-Sept 2017}
\workitemTwo
{Analysed customer's submitted documentation (address and/or ID) on the system to check for the reasons of failiure and offered alternative solutions to re-submit documentation to customers. 
}
{Helped customers solve technical issues when trying submitting documents using the online method by diagnosing the problem/s.}



\datedsubsection{Operations-Executive, Aegis Outsourcing UK, Experian
}{Jul 2015--Sept 2015}

\workitemTwo
{Answered customer queries regarding credit report status which required me to be concise and clear with my communication whilst maintaining a good telephone manner.
}
{Assisted customers with signing-up for the credit check service and related technical issues, if any. 
}

%\datedsubsection{Operations-Executive, Swinton Insurance
%}{Jul 2015--Sept 2015}




\section{Technology Skills}
\begin{itemize}
  \item Java - Created various programs during year 1 to learn through application the various concepts such as polymorphism, inheritence and data structures. 
  \item Python -  Created a server and a client in python to build a chat application. 
  \item C - Currently building programs in C to study the behaviour, complexity and correctness of algorithms.
  \item Microsoft Office Package - Proficient
   \end{itemize}
  \paragraph{Continuation of Technology Skills Section} 
  \begin{itemize}
  \item HTML - Used HTML to create the front end of the Coffee Time application.
  %\item Testing - created tests before writing and execution of java programs and to make bugs in programs to become prominent to locate the whereabouts 
  \item Command line
  \item Git - utilised during the building of the Coffee Time application which prevented clashing and rewriting of code and allowed recovery if a problem in the code arised. 
  \item MAC OSX, Windows, Linux
  \item Latex - Used to create project reports, this was advantageous to learn as I continue to create documents    using Latex for ease of structuring. 
  \item Verilog - Used to test and build components of the processor,MU0, duruing 1st year, Currently using this to create the design of the Stump processor.
  \item CAD tools - Used to build higher level schematic desgins of processor components. 
  \item Dia - Utilsed to create extended entity relationship diagrams to represent databases in conceptual form.
  \item Eclipse - Currently using for the Stendhal project. 
  \item Assembly Language
\end{itemize}

\section{Positions of Responsibility}

%\datedsubsection{STEM ambassador}
%{Oct 2017-Present }
%\workitemTwo
%{Met with donors (Alumni)}
%{Conversed with them about how their scholarship helped us, scholarship ambassadors (recipients), with the academic year and about our university experience till date. 
%}

\datedsubsection{Health and Safety Student Representitive}{Oct 2017-Present}

\workitemOne
{Approached and liaised with customers in a friendly manner whilst assisting them with their queries and advising them on available items.
}

\datedsubsection{Computer Science Student Representative }
{Oct 2017-Present }
\workitemFour
{Voted from a large number of students to represent Year 2.}
{Acting as a bridge between peers and staff at the school of Computer Science.}
{Cooperating and Conversing with peers to understand and gather feedback of what needs to be improved and/or refined.}
{Relaying opinions and views of peers and passing my own (if applicable) to staff.}


\datedsubsection{PASS Leader (Peer Assisted Study Sessions)}
{Oct 2017-Present }
\workitemThree
{Facilitating the learning of year 1 students and helping them with any academic and non-academic issues. }
{Planning, Structuring and leading fun and interative sessions with other PASS leaders.}
{Triggering peer to peer interations to give rise to shared learning}

\datedsubsection{Scholarship Ambassador - University of Manchester}
{Sept 2016-Present }
\workitemThree
{Selected to represent scholarship recipients.}
{Met with donors (Alumni)}
{Conversed with them about how their scholarship has helped us with the academic year and about our university experience till date. Also provided tours to Alumni at request. 
}


\section{Awards, skills and other qualifications}


\subsection{Languages}
\begin{tabular}{l l l l}
English(bilingual proficiency) & Urdu(fluent) &  Katchi(native proficiency) 
\end{tabular}


\end{document} 